\chapter{Requirements}
The requirements for the different parts of the project were about the requirements for the application, the underlying model and content provider, and the documentation for the model and content provider. 

\section{Final requirements}
Several meetings with the customer and health experts led the initial requirements to be out of date and a little vague which led to new and updated requirements.

\subsection{Functional requirements}
\begin{itemize}
\item An Android content provider that stores and makes the data available for other applications through an API. The content provider shall has the ability to show requested data apropiatly without any loss of information and in the way how the user wishes
\begin{itemize}
\item Measure gait speed: The application shall be able to detect the speed of the users gait so that this information can used as a element in the whole detection process. Thus the costumer required in order to detect the main parameter for falling.
\item Measure gait variability: The application shall be able to detect the variability of the users gait. That will be one of the main part for understanding its fall behaviour and the reasons of his falling down. Thus the costumer required in order to detect the main parameter for falling.
\item Measure steps: The ability to counting the steps in order to use their amount as a parameter for the walk/fall statistic.
\item Filter out noise in terms of bad and unnatural movements.
\end{itemize}
\item An example application that can visualize this data and represent them in a pedagogical manner.
\begin{itemize}
\item Ability to do self-tests: This functionality shall give a feedback for the user. Thus the costumer required in order to include the user in the health process.
\begin{itemize}
\item Reaction speed: This application shall give the time of the users reaction to include it in the detection.
\item Stand up sit down capability
\item Balance tests: This part of the application is to understand the balance of the user to include it in the detection.
\end{itemize}
\end{itemize}
\item Documentation on the content provider that can be referred to
\end{itemize}	

\subsection{Nonfunctional requirements}
\begin{itemize}
\item 80\% of the elderly should manage to use the app within 10 minutes of education given that they have some prior knowledge of smartphones.
\item Midly visually impaired should be able to use the application.
\item Color blind should be able to use the application. These shall fulfilled for the reason that the application shall fulfiill the requirement of easy-usability.
\end{itemize}	


\section{Understanding the requirements}

The requirements were specified after several meetings with the customer. The understanding the group had of the requirements before meeting the customer was not sufficient to create a set of requirements. The requirements were also subject to change as the project progressed. \\

The meetings served their purpose, and filled in a lot of holes that were missing from the preliminary description:
\begin{itemize}
\item The development process in question \footnote{See Chapter \ref{def:devProcess} for a description of the development process} uses a iterative approach. This essentially means that the requirements expands as the time goes, and to define the requirements from the beginning is impossible. This decision was made in collaboration with the customer.
\item The team at SINTEF got a wide range of experts to help the group with health-specific features, e.g. making the algorithms to recognize movements.
\item The customer expected weekly meetings with the whole group present, and that goals had been achieved before each meeting. At each meeting a new goal was set.
\end{itemize}

\section{Initial requirements}

According to the project description, the following should be developed:
\begin{itemize}
\item A model of physical movements based on common movement sensors found in Android smart phones.
\item An Android content provider that stores and makes available the data in this model through an Application Programming Interface(API).
\item An example application that can visualize this data. Thus for making the result visible and transparent.
\end{itemize}
\section{License}
The results of the project was intended to be released under the Apache 2.0 license. It is an open source license, which can be found  at the following web site: \url{http://www.apache.org/licenses/LICENSE-2.0.html}\\
Highlights of what can, cannot and must be done under the license is described here:\\
\textbf{Must be done}
\begin{itemize}
\item include copyright
\item include the license
\item state what changes has been made
\end{itemize}
\textbf{What can be done}
\begin{itemize}
\item use copies of the licensed work without paying
\item use the content with commercial products later
\item modify the licensed work as desired
\item the work can be distributed as desired
\end{itemize}
\textbf{Cannot do}
\begin{itemize}
\item trademark the licensed work
\end{itemize}
The specific terms can be found at the mentioned address, and has also been included in the appendix, see \ref{appendix:license}, along with License and Notice files.

%\section{Testing}
%The tests were done by the black-box principle of testing, meaning that all the tests consider is, with no attention given to the inner workings of the methods. Because of the team following an agile development method, it was possible to create and test test-cases in short order. The test-cases were therefore written with results included.
%The tests are corresponding screens for the tests were as follows:
%\begin{description}
%\item[Name Entry] is associated with tests 1.x, both when program is started the first time, and when name-change is initiated from settings.
%\item[Event Details Screen] is associated with tests 2.x.
%\item[Statistics Screen] is associated with tests 3.x.
%\item[Clear history] can be initiated from settings screen and is associated with tests 4.x.
%\item[Related people Screen] is associated with tests 5.x. 
%\end{description}
%
%\begin{figure}[h]
%\label{tab:testList}
%\caption{List of tests for the application}
%\begin{tabular}{|p{\textwidth /4}||p{\textwidth /4}|p{\textwidth /4}|p{\textwidth /4}|}
%\hline
%Test number & Input value& Actual Result& Expected Result \\
%\hline
%\hline 
%1.1 & Any valid name & Hello: + name & Hello: + name \\ 
%\hline 
%1.2 & Empty name-box & Hello: &Hello:  \\ 
%\hline 
%2.1 & Remove event button clicked & Event removed & Event removed \\ 
%\hline 
%2.2 & Keep event button clicked & Event is kept & Event is kept \\ 
%\hline 
%3.1 & Timeslot set to 10 min or less & Data from correct timeslot displayed & Data from correct timeslot displayed \\ 
%\hline 
%3.2 & • & • & • \\ 
%\hline 
%4.1 & Clear History Button Clicked & History Cleared & History Cleared \\ 
%\hline 
%5.1 & Add existing contact button clicked & Contact shows up on appropriate screen  & Contact shows up on appropriate screen \\ 
%\hline 
%5.2 & Create New Contact function used & New Contact shows up on appropriate screen & New Contact shows up on appropriate screen \\ 
%\hline 
%
%\end{tabular} 
%\end{figure}
