The following is a list of the sprints:

\begin{description}
\item[Sprint 1: 01.02.13 - 08.02.13] \hline \hfill \\
User stories and paper prototypes of the GUI were developed.
\item[Sprint 2: 08.02.13 - 15.02.13] \hline \hfill \\
The group focused on learning Android development. New GUI paper prototypes were developed based on customer feedback. A mock-up application demonstrating core parts of the GUI was developed.
\item[Sprint 3: 15.02.13 - 22.02.13] \hline \hfill \\
Continued efforts on learning Android development. The mock-up was developed further. Research was conducted on the application domain, and on related applications. 
\item[Sprint 4: 22.02.13 - 01.03.13] \hline \hfill \\
The prototype application was expanded with a database, GUI visuals were improved, menu usage was made consistent throughout the prototype. The group tried to familiarize themselves with Content Providers in Android.
\item[Sprint 5: 01.03.13 - 08.03.13] \hline \hfill \\
A Content Provider was developed, incorporated the step detection from the Pedometer open-source application. Some secondary screens (settings and statistics) were implemented. Basic widget created.
\item[Sprint 6: 08.03.13 - 15.03.13] \hline \hfill \\
Widget was connected successfully to the main application. Application connected to the Content Provider. Work on report for the mid-term hand-in. Presentation for the focus group prepared. Unsuccessful attempts at making the Pedometer/Content Provider location aware. Implementation of contact management. 
\item[Sprint 7: 15.03.13 - 22.03.13] \hline \hfill \\
Research and development of step detection algorithm: Sensor data collection application developed, python scripts for displaying data and prototyping of algorithm. Work on Javadoc and code re-factoring. Correction of report based on mid-term feedback.
\item[Ester holidays: 23.03.13 - 02.04.13] \hline \hfill \\
Little work was done due to the holidays.
\item[Sprint 9: 03.04.13 - 05.04.13] \hline \hfill \\
New system architecture was designed. Step detection algorithm implemented as Android application. The old Content Provider/Pedometer discarded, and new Content Provider implemented. 
\item[Sprint 10: 05.04.13 - 12.04.13] \hline \hfill \\
Efforts were focused on bug-fixing and integration of the three components. 
\item[Sprint 11: 13.04.13 - 19.04.13] \hline \hfill \\
Work on final report and small adjustments the integration of the components. The code underwent re-factoring and commenting. 
\end{description}